Inference for multivariate peaks over threshold models

### 2021-09-15 evaluation.tex
evaluation edits

\subsection{Posterior Predictive Loss Criterion}
The posterior predictive loss criterion, \emph{PPL} is introduced in \cite{gelfand1998}.  When we
  assume a squared error loss function, then for the $i$th observation, the posterior predictive
  loss criterion is computed as
  \begin{equation}
    \label{eq:ppl}
    D_{k}^{(i)} = \text{Var}\left(X_i\right) + \frac{k}{k + 1}\left(\text{E}[X_i] - x_i\right)^2,
  \end{equation}
  where $X_i$ is a random variable from the posterior predictive distribution for $x_i$.  The
  scalar $k$ is a weighting factor by which we arbitrarily scale the importance of goodness of fit
  relative to precision.  In our analysis, we take the limit as $k\to\infty$, weighting both
  parts equally.  Interpreting this criterion, a smaller $\text{Var}(\bm{X}_l)$ indicates a higher
  precision, and a smaller $(\text{E}[\bm{X}_l] - \bm{x}_l)^2$  indicates a better fit.  Thus,
  smaller is better.  Note that this is defined for a univariate distribution.  As we are dealing
  with a multivariate distribution, we will be taking the posterior predictive loss
  summed over all dimensions.  That is,
  \begin{equation}
    \label{eq:ppl2}
    D_k^{(i)} = \frac{1}{d}\sum_{l = 1}^{d}\left[\text{Var}(X_{il}) + \frac{k}{k+1}\left(\text{E}[X_{il}] - x_{il}\right)^2\right]
  \end{equation}
  Then we report the average $D_k$, taken over all $i$.

\subsection{Energy Score}
The energy score of Gneiting, et al\cite{gneiting2007}, is a generalization of the continuous ranked
  probability score, or \emph{crps}, defined for a multi-dimensional random variable.
  \begin{equation}
    \label{eq:es}
    \text{ES}\left(P,x_i\right) =  \text{E}_p g\left(\bm{X}_i, \bm{x}_i\right) - \frac{1}{2}\text{E}_p g\left(\bm{X}_i,\bm{X}_i^{\prime}\right)
  \end{equation}
  where $g(\cdot)$ identifies a negative definite kernel, and $\bm{X}_i^{\prime}$ represents another
  replicate from the posterior predictive distribution of $\bm{x}_i$. A function $g$ is a negative definite kernel if it is symmetric in its arguments, $g(x_1,x_2) = g(x_2,x_1)$, and for which
  $\sum_{i =1}^n\sum_{j=1}^n\alpha_i\alpha_jg(x_1,x_2) \leq 0$ for all positive integers n, with the
  restriction that $\sum_{i=1}^n\alpha_i = 0$.  Euclidean distance is one example of a negative definite kernel,
  and the one most often used.  However,   on $\mathcal{S}_p^{d-1}$ for $p > 1$, Euclidean distance
  can under-report the actual distance required for travel between two points. That distortion is
  maximized on $\mathcal{S}_{\infty}^{d-1}$.

@@

\begin{prop}
For points $a,b \in \mathcal{S}_{\infty}^{d-1}$ a valid negative definite kernel can be formed as
  \begin{equation}
    g(\bm{a},\bm{b}) = \begin{cases}
        \pnorm{\bm{b}-\bm{a}}{2} &\text{ if }\argmax_l\bm{a} = \argmax_l\bm{b}\\
        \pnorm{\bm{c}-\bm{a}}{2} + \pnorm{\bm{b}-\bm{c}}{2} &\text{ otherwise}
    \end{cases}
  \end{equation}
  where $\bm{c}$ resides on the intersection between the faces of $\bm{a}$ and $\bm{b}$, and minimizes $g(\bm{a},\bm{b})$.
\end{prop}

@@

To compute this energy score as described would require optimization of the interim point $\bm{c}$.
  If we again consider the one-dimensional rotation in Equation~\ref{eq:1drotation}--we
  can view that as a numerically easier analogue accomplishing the same goal: the distance from
  the starting point, to some optimal point along the intersection between the starting and
  ending faces, to the ending point.  The strait line will pass through the optimal point, so
  the optimization of the interim point is accomplished \emph{en passant}.

>>>>

\subsection{Posterior Predictive Loss Criterion}
The posterior predictive loss criterion, \emph{PPL} is introduced in \cite{gelfand1998}.  When we
  assume a squared error loss function, then for the $i$th observation, the posterior predictive
  loss criterion is computed as
  \begin{equation}
    \label{eq:ppl}
    D_{k}^{(i)} = \text{Var}\left(X_i\right) + \frac{k}{k + 1}\left(\text{E}[X_i] - x_i\right)^2,
  \end{equation}
  where $X_i$ is a random variable from the posterior predictive distribution for $x_i$.  The
  scalar $k$ is a weighting factor by which we arbitrarily scale the importance of goodness of fit
  relative to precision.  In our analysis, we take the limit as $k\to\infty$, weighting both
  parts equally.  Interpreting this criterion, a smaller $\text{Var}(\bm{X}_{\ell})$ indicates a higher
  precision, and a smaller $(\text{E}[\bm{X}_{\ell}] - \bm{x}_{\ell})^2$  indicates a better fit.  Thus,
  smaller is better.  Note that this is defined for a univariate distribution.  As we are dealing
  with a multivariate distribution, we will be taking the posterior predictive loss
  summed over all dimensions.  That is,
  \begin{equation}
    \label{eq:ppl2}
    D_k^{(i)} = \frac{1}{d}\sum_{\ell = 1}^{d}\left[\text{Var}(X_{i,\ell}) +
                  \frac{k}{k+1}\left(\text{E} [X_{i,\ell}] - x_{i,\ell}\right)^2\right]
  \end{equation}
  Then we report the average $D_k$, taken over all $i$.

\subsection{Energy Score}
The energy score of Gneiting, et al\cite{gneiting2007}, is a generalization of the continuous ranked
  probability score, or \emph{crps}, defined for a multi-dimensional random variable.
  \begin{equation}
    \label{eq:es}
    \text{ES}\left(P, \bm{x}_i\right) =  \text{E}_p g\left(\bm{X}_i, \bm{x}_i\right) -
                                    \frac{1}{2}\text{E}_p g\left(\bm{X}_i,\bm{X}_i^{\prime}\right)
  \end{equation}
  where $g(\cdot)$ identifies a negative definite kernel, and $\bm{X}_i^{\prime}$ represents another
  replicate from the posterior predictive distribution of $\bm{x}_i$. A function $g$ is a negative definite kernel if it is symmetric in its arguments, $g(x_1,x_2) = g(x_2,x_1)$, and for which
  $\sum_{i =1}^n\sum_{j=1}^n\alpha_i\alpha_jg(\bm{x}_1,\bm{x}_2) \leq 0$ for all positive integers n, with the
  restriction that $\sum_{i=1}^n\alpha_i = 0$.  Euclidean distance is one example of a negative definite kernel,
  and the one most often used.  However, on $\mathcal{S}_p^{d-1}$ for $p > 1$, Euclidean distance
  can under-report the actual distance required for travel between two points. That distortion is
  maximized on $\mathcal{S}_{\infty}^{d-1}$.

@@

\begin{prop}
For points $a,b \in \mathcal{S}_{\infty}^{d-1}$ a valid negative definite kernel can be formed as
  \begin{equation}
    g(\bm{a},\bm{b}) = \begin{cases}
        \pnorm{\bm{b}-\bm{a}}{2} &\text{ if }\argmax_{\ell}\bm{a} = \argmax_{\ell}\bm{b}\\
        \pnorm{\bm{c}-\bm{a}}{2} + \pnorm{\bm{b}-\bm{c}}{2} &\text{ otherwise}
    \end{cases}
  \end{equation}
  where $\bm{c}$ resides on the intersection between the faces of $\bm{a}$ and $\bm{b}$, and minimizes $g(\bm{a},\bm{b})$.
\end{prop}

@@

To compute this energy score as described would require optimization of the interim point $\bm{c}$.
  If we again consider the one-dimensional rotation in Equation~\ref{eq:1drotation}---we
  can view that as a numerically easier analogue accomplishing the same goal: the distance from
  the starting point, to some optimal point along the intersection between the starting and
  ending faces, to the ending point.  The strait line will pass through the optimal point, so
  the optimization of the interim point is accomplished \emph{en passant}.
